---
title: "Write own script then save"
output: 
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Follow instructions below, then save the file. Once this is done,follow [06_saving_permanent_copy.md](https://github.com/rmp15/rstudio_cloud_tutorial/blob/main/basics/06_saving_permanent_copy.md) to save your own adapted copy of this GitHub Repository!

### Create a vector called vector_1 with elements 101,102,103,104,105
```{r}
vector1<-c(101,102,103,104,105)
```

### Print how many elements vector_1 has
```{r}
print(length(vector1))
```

### Third element of vector_1
```{r}
print((vector1[3]))

```

### Second and fourth element of vector_1
```{r}
print((vector1[c(2,4)]))
```

### Access all but first element of vector_1
```{r}
print((vector1[-1]))
```

### Take elements of vector_1 less than 104
```{r}
vector1[vector1<104]
```

### Modify vector_1 2nd element
```{r}
vector1[2]<-8563265852
```

### Modify vector elements less than 104 to be -1
```{r}
vector1[vector1<104]<- -1
```

### Modify vector elements less than 9 to be -1
```{r}
vector1[vector1<9]<- -1
```

## Once you have filled in the questions, try 'Knitting' via the button in the toolbar above this window
